\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-30 syntax.tex
escape

\centering
\captionsetup{justification=centering}

\caption{Seal Judgement, and its Agda Representation \\ (or What do we mean when we say one judgement is a shorthand for the other)}

\begin{minted}[escapeinside=@@]{agda}
Seal : (Γ : Con) → (σ : Sig Γ n) → (A : Ty Γ) → Set 
Seal Γ σ A = Tm (Γ, 𝓒σ) A[π₁]

@@

idₛ : Seal Γ σ 𝓒σ
idₛ = π₁
\end{minted}

>>>>

\medskip

\begin{minted}[escapeinside=@@]{agda}
Seal : (Γ : Con) → (σ : Sig Γ n) → (A : Ty Γ) → Set 
Seal Γ σ A = Tm (Γ, @$\mathcal{C}$@σ) A[π₁]

@@

idₛ : Seal Γ σ @$\mathcal{C}$@σ
idₛ = π₁
\end{minted}

\caption{Seal Judgement, and its Agda Representation (or What do we mean when we say one judgement is a shorthand for the other)}
